### 2016-09-29 results.tex
GBF
cheers

\todo{OW privacy proof?  Distributional SS privacy proof?}

@@

\begin{figure}
\centering
\fpage{.425}
{
\adversaryv{$A^{\TestOracle}(\pubaux)$}\\[1ex]
$M \gets \pubaux$\\
for $1 \leq i_1 < i_2 < \cdots < i_k \leq m$\\
\nudge $x \gets M[i_1] \xor M[i_2] \xor \cdots \xor M[i_k]$\\
\nudge if  $x \not\in S \wedge \left(\bigwedge_{j=1}^k H(j,x)=i_j \right)$ then \\
\nudge\nudge $a\gets\TestOracle(x)$\\
\nudge\nudge Return $\bot$\\
}
%{
%\adversaryv{$A^{\TestOracle}(\pubaux)$}\\[1ex]
%$M \gets \pubaux$\\
%for $1 \leq i_1 < i_2 < \cdots < i_k \leq m$\\
%\nudge $x \gets M[i_1] \xor M[i_2] \xor \cdots \xor M[i_k]$\\
%\nudge if $\TestOracle(x)=1$ then Return $\bot$
%}
%\caption{Adversary for Theorem~\ref{thm:xxx}.  \textbf{Left:} public hash case, \textbf{Right:} private hash case.}
\caption{Adversary for Theorem~\ref{thm:xxx}. }
\label{fig:adv-gbf}
\end{figure}
Dong, Chen and Wen~\cite{xxx} introduce a set-membership data
structure called a \emph{garbled Bloom filter} (GBF).   Modulo some implementation
details, a GBF is like a classical Bloom filter, but
rather than storing a bit 1 at the indices determined by $H_j(x)$, the
GBF stores xor-shares of~$x$.  Thus, if $x \in S$, then hashing~$x$
and xoring together the strings stored at the indicated positions
recovers~$x$. We give the pseudocode for the GBF $\Rep$ and $\Qry$
algorithms in Figure~\ref{fig:gbf}.

@@

Now, this adversary will find a false positive, if there is one, but in the worst case it will consider
$\binom{m}{k} \approx m^k$ $k$-tuples of positions.  If both~$m$
and~$k$ are large this is infeasible.  In~\cite{xxx} they suggest to
set~$k=\lambda$, and test with $\lambda=80$.  Making 80 hash calls per
set-membership query would be laughable in many applications, and a
$2^{-80}$ false-postive rate would be considered overkill.\footnote{Note
that, as described in~\cite{xxx}, $\lambda$ must be at least the
bitlength of the longest element $x \in S$. \tsnote{This could be
  handled with a slight change to the set membership test, by checking
if the $\lambda$-bit shares xor to, say, the $\lambda$-bit truncation
of~$x$.}}
Let us consider a practically interesting set of parameters. Say you have a 1000-position
filter, $m=1000$, and a 100-element set, $n=100$,  and $k=4$ hash
functions (a la Squid\cite{squid}).  This results in a false-positive rate of
approximately 1\% in a classical BF.  There are roughly $2^{35}$
subsets of four indices to consider, which is reasonable on a laptop
these days.  Moreover, with $n=100$ the expected
number of trials is roughly $2^{28}$.
Note that the attack is easily extended to find $r>1$ false positives.

@@

@@

\heading{Privacy. }
\begin{itemize}
\item Prove that the basic BF, in the ROM, is private.  \tsnote{Not SS, should be OW}
\item Show that the bigram DS-PRF construction is SS \tsnote{Shows Neidermayer's suggested countermeasure works}
\item Show that the basic BF DS-PRF construction is SS [DONE]
\item Prove privacy bounds for the constructions from NY \tsnote{Follows from Jon's meta-theorem}

@@

\item Attack priv-security of Dong, Chen, Wen ``garbled Bloom Filter'' construction when the hash functions are public.\tsnote{I give the attack in the related work section.  Copy it here and flesh it out.}  Prove priv-security privacy of construction when hash functions are secret.  \tsnote{Makes the point that the application setting really matters.}

>>>>

\todo{OW privacy proof? [JON]}

@@

\begin{figure}[t]
\centering
\fpage{.425}
{
\adversaryv{$A^{\TestOracle}(\pubaux)$}\\[1ex]
$M \gets \pubaux$\\
for $1 \leq i_1 < i_2 < \cdots < i_k \leq m$\\
\nudge $x \gets M[i_1] \xor M[i_2] \xor \cdots \xor M[i_k]$\\
\nudge if  $x \not\in S \wedge \left(\bigwedge_{j=1}^k H(j,x)=i_j \right)$ then \\
\nudge\nudge $a\gets\TestOracle(x)$\\
\nudge\nudge Return $\bot$\\
}
%{
%\adversaryv{$A^{\TestOracle}(\pubaux)$}\\[1ex]
%$M \gets \pubaux$\\
%for $1 \leq i_1 < i_2 < \cdots < i_k \leq m$\\
%\nudge $x \gets M[i_1] \xor M[i_2] \xor \cdots \xor M[i_k]$\\
%\nudge if $\TestOracle(x)=1$ then Return $\bot$
%}
%\caption{Adversary for Theorem~\ref{thm:xxx}.  \textbf{Left:} public hash case, \textbf{Right:} private hash case.}
\caption{Attack for garbled Bloom filters with public~$M$. }
\label{fig:adv-gbf}
\end{figure}
Dong, Chen and Wen~\cite{xxx} introduce a set-membership data
structure called a \emph{garbled Bloom filter} (GBF).   Modulo some implementation
details, a GBF is like a classical Bloom filter, but
rather than storing a bit 1 at the indices determined by $H_j(x)$, the
GBF stores xor-shares of~$x$.  Thus, if $x \in S$, then hashing~$x$
and xoring together the strings stored at the indicated positions
recovers~$x$. We give the pseudocode for the GBF $\Rep$ and $\Qry$
algorithms in Figure~\ref{fig:gbf}.

@@

Now, this adversary will find a false positive, if there is one, but in the worst case it will consider
$\binom{m}{k} \approx m^k$ $k$-tuples of positions.  If both~$m$
and~$k$ are large this is infeasible.  In~\cite{xxx} they suggest to
set~$k=\lambda$, and test with $\lambda=80$.  Making 80 hash calls per
set-membership query would be laughable in many applications, and a
$2^{-80}$ false-postive rate would be considered overkill.\footnote{Note
that, as described in~\cite{xxx}, $\lambda$ must be at least the
bitlength of the longest element $x \in S$. \tsnote{This could be
  handled with a slight change to the set membership test, by checking
if the $\lambda$-bit shares xor to, say, the $\lambda$-bit truncation
of~$x$.}}
Let us consider a practically interesting set of parameters. Say you have a 1000-position
filter, $m=1000$, and a 100-element set, $n=100$,  and $k=4$ hash
functions (a la Squid\cite{squid}).  This results in a false-positive rate of
approximately 1\% in a classical BF.  There are roughly $2^{35}$
subsets of four indices to consider, which is reasonable on a
commodity laptop.  Moreover, with $n=100$ the expected
number of trials is roughly $2^{28}$.
Note that the attack is easily extended to find $r>1$ false positives.

@@

\todo{Public M, ROM (no, empty priv)}\tsnote{one-wayness suffers the same
  attack as correctness, I think?}

\todo{Public M, PRF hash (follows from meta-theorem)}

\todo{Private M (trivial!)}

@@

\heading{Privacy. }
\begin{itemize}
\item Prove that the basic BF, in the ROM, is private.  \tsnote{Not SS, should be OW}
\item Show that the bigram DS-PRF construction is/isn't SS [DONE]
\item Show that the basic BF DS-PRF construction is SS [DONE]
\item Prove privacy bounds for the constructions from NY \tsnote{Follows from Jon's meta-theorem}

@@

\item Attack correctness of Dong, Chen, Wen ``garbled Bloom Filter'' construction when the hash functions are public.\tsnote{I give the attack in the related work section.  Copy it here and flesh it out.}  Prove priv-security privacy of construction when hash functions are secret.  \tsnote{Makes the point that the application setting really matters.}
